\newenvironment{prettylist}{
	\begin{list}{
		\footnotesize\raisebox{0pt}{\small\ding{121}}
	}{
		\setlength\topsep{2pt plus 1pt minus 1pt}
		\setlength\leftmargin{2em}
		\setlength\rightmargin{0pt}
		\setlength\itemsep{1pt plus.1pt}
		\setlength\parskip{0pt}
		\setlength\parsep{0pt}
		\setlength\itemindent{0pt}
	}
}{
	\end{list}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% These are the general sections to include.  %
%                                             %
% You can alter some names, but follow the    %
% suggestions in the NSF guidelines.          %
%                                             %
% If spacing is tight, play with negative     %
% vspaces w/in the text to reduce whitespace. %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 1: Introduction    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{intro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2: Overview        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{background}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 3: Research Plan   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{methodology}

\section{Conclusion}

These three works, Jetset, \emph{Story Beyond the Eye}, and InteGreat, present three novel perspectives on the recovery of models from binary code.
In the first, the models were expression sets corresponding to the constraints of hardware peripheral interactions.
The second involved the more complex extraction and hand-modeling of glyph shifting schemes used to determine the information leaked by redacted text.
Finally, the third presented a more formal and sophisticated model for the extraction of meaningful abstractions from symbol-stripped, binary code.

As a whole, these works indicate a number of hard problems in the domain of binary program analysis, including the resolution and modeling of precise, discrete floating point operations and their relationship to the real domain, the ability to avoid difficulties incurred in developing a general solution to the halting problem through the use of abstraction, and the impossibility of perfectly rehosting a firmware image into an emulator and accurately interacting with it without \emph{some} knowledge of physical factors and additional hardware that plays a role in the system.

However, the resulting publications also make significant strides towards identifying the proper responses to each of these problems through the use of abstraction, careful evaluation of the algorithms under study, consideration of microarchitectural semantics, and novel binary analysis techniques.
The proposed dissertation will work to unify these findings and present them within a framework that is at once both detailed, empirically justified, clear, and unified.
It will also work to outline the core limitations of these works, and therefore provide useful commentary for future work in the domain of binary program analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 4: Management Plan %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Line}

As the present author has present commitments for employment regardless of the outcome of his doctoral work, the dissertation will be subject to practical constraints on time in accordance with the current University of Illinois policies on dissertation timelines.
The absolute minimum time between the preliminary exam proposal and defense is four months, and the current scheduled date of the exam is February 24th.
As a result of aforementioned employment constraints, the present author intends to complete the writing of the defense by July 2023 and the proposed defense will occur at the end of this same month, the schedules of the defense committee permitting and considering all other university requirements have been fulfilled.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 5: Science Merit   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scientific Merit}

The extensive efforts of four years of research culminating the in the present proposal have resulted in three redistributable systems for accomplishing scientifically relevant research.
All the code for the Jetset system has already been made publicly available and contains findings and algorithms that may be repurposed for other work.
While \emph{Story Beyond the Eye} did not release a portion of its code base due to the ethical dangers involved, the work released likely the most precise library for recovering and interacting with the rendering specifications of PDF text yet created---its accuracy was better than several proprietary tools evaluated while conducting the paper's research--, at least at the time of writing.
Finally, the InteGreat system provides users with a specification language for developing increasingly sophisticated lifters for symbol-stripped binary firmware.

Beyond their acceptance and submission to top conferences, the systems presented in this proposal each present novel findings in their respective domains. 
The Jetset work was the first to apply symbolic execution to rehost firmware images across multiple architectures.
\emph{Story Beyond the Eye} discovered novel information leaks in text redactions of PDF documents.
InteGreat introduced a new ideas, nested abstraction specification and firmware model extraction, to the subject of verifying embedded system firmware.

These works also addressed and identified problems in their respective subdomains.
Jetset provided a symbolic executor for QEMU and identified the issue of supporting TCG helper functions when evaluating the emulation of embedded systesm.
\emph{Story Beyond the Eye} presented several possible defenses against redaction attacks, and released these defenses, as well as a .
Finally, InteGreat presented a system for verifying the behavior of an implementated firmware image by lifting it to a more abstract representation that could be paired with systems like DryVR~\cite{fan2017dryvr}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 6: Impact/Outreach %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Broader Impacts}

With respect to scientific communities, the three works in question have already sparked discussion.
The Jetset Work has recieved, at the time of writing, 24 citations over the course of two years, and continues to spur emails with questions regarding the paper.
While the PETS 2023 camera ready has not yet passed, algorithms for redaction location used by \emph{Story Beyond the Eye} have already been requested by multiple researchers and the preprint publication has recieved citation~\cite{rust2022language}.
Finally, the InteGreat work has recieved extensive distribution within Cymanii, a Department of Energy funded organization, and Sandia National Laboratories due to InteGreat's multiple potential applications to the analysis of cyberphysical systems.

In terms of practical impact, the two accepted conference publications have induced direct responses from affected parties.
Jetset's core finding, an exploit for the CMU-900's operating system, resulted in direct communications with avionics manufacturers on the security of their systems.
The work on deredaction resulted in the discovery of hundreds of broken redactions, notifications of several affected parties, including the US Courts, and actions on behalf of several of these parties to prevent future information leaks. 
Moreover, the prepublication of the latter work has spurred popular press, and induced a journalist to publish a story on the findings for Wired Magazine~\cite{wiredredact}.
